---
title: "Hackathon_Phase1"
author: "Abhirupa Lodh"
date: "10 November 2017"
output: html_document
---

```{r}
library(tree)
library(e1071)
library(class)
library(randomForest)
library(corrplot)
```


```{r}
setwd("C:/Users/Administrator/Desktop/Machine Learning/Hackathon/Phase 1")
```

```{r}
getwd()
```


```{r}
sample_data <- read.csv("C:/Users/Administrator/Desktop/Machine Learning/Hackathon/Phase 1/Model_Data.csv")
summary(sample_data)
```

```{r}
r=nrow(sample_data)
c=ncol(sample_data)
r
c
```

```{r}
str(sample_data)
```

#Data Imputation 

```{r}
#code  for finding mode 

Mode <- function(v) {
  uniqv <- unique(v)
  uniqv[which.max(tabulate(match(v, uniqv)))]
}
```

#workclass , occupation and native.country has empty values as " ?"

Step 1: Convert then to character and impute
step 2: Convert them again to factors

```{r}
as.character(sample_data$workclass)->sample_data$workclass
as.character(sample_data$occupation)->sample_data$occupation
as.character(sample_data$native.country)->sample_data$native.country
```

```{r}
sample_data$workclass[sample_data$workclass==" ?"]=Mode(sample_data$workclass)
sample_data$occupation[sample_data$occupation==" ?"]=Mode(sample_data$occupation)
sample_data$native.country[sample_data$native.country==" ?"]=Mode(sample_data$native.country)
```

```{r}
as.factor(sample_data$workclass)->sample_data$workclass
as.factor(sample_data$occupation)->sample_data$occupation
as.factor(sample_data$native.country)->sample_data$native.country
```

```{r}
str(sample_data)
```

#native.country has 41 lavels. Convert it to numeric

```{r}
as.numeric(sample_data$native.country)->sample_data$native.country
```

```{r}
levels(sample_data$compensation)

as.character(sample_data$compensation)->sample_data$compensation


```

```{r}
sample_data$compensation[sample_data$compensation==" >50K."]=" >50K"
sample_data$compensation[sample_data$compensation==" <=50K."]=" <=50K"
```

```{r}
as.factor(sample_data$compensation)->sample_data$compensation
```


Looking for variable correlation 

```{r}
corr_data=sample_data[,c('age','fnlwgt','education.num','capital.gain','hours.per.week')]

```

```{r}
cor(corr_data)
```

```{r}

corrplot(cor(corr_data),method = "color",order = "hclust")
```

#All the attributes seems to be independent of  each other

```{r}
set.seed(0040)
index=sample(c(1:r),size = 0.8*r,replace = F)
train=sample_data[index,]
test=sample_data[-index,]
```

#Model1 : Decision Tree

#sex+native.country+race+capital.loss+capital.gain -> 81.28906
#sex+native.country+race+capital.loss+capital.gain,fnlwgt -> 81.28906
#sex+native.country+capital.loss+capital.gain -> 81.28906
#sex+native.country+capital.loss+capital.gain,fnlwgt -> 81.28906
#compensation~education+relationship+capital.gain -> 84.83073
#compensation~education+relationship+capital.gain+sex -> 84.83073
#compensation~. -> 84.83073
#compensation~hours.per.week+capital.gain -> 80.02604
#compensation~hours.per.week+education+relationship -> 82.23958
#compensation~hours.per.week+education -> 78
#compensation~hours.per.week+relationship -> 77.34375
#compensation~hours.per.week+capital.gain-> 80.02604
#compensation~hours.per.week+capital.loss+capital.gain->81.41927

```{r}
model1=tree(compensation~.,data=train)
```

```{r}
pred=predict(model1,test)
```


```{r}
maxidx=function(arr){
  return(which(arr==max(arr)))
}
idx=apply(pred,c(1),maxidx)
modelpred=c(" <=50K"," >50K")[idx]
confmat=table(modelpred,test$compensation)

#modelpred
confmat
```

```{r}
accuracy=sum(diag(confmat))/nrow(test)

paste("Accuracy Decision Tree : ",accuracy*100)
```

#Model2 : Naive Bayes

```{r}
model2=naiveBayes(compensation~.,data=train)
```

```{r}
pred=predict(model2,test)
```

```{r}
table(test$compensation,pred)->acc_mat
acc_mat
```

```{r}
accuracy=sum(diag(acc_mat))/nrow(test)
paste("Accuracy Naive Bayes : ",accuracy*100)
```

#kNN 

```{r}
sample_data->sample_data_k
str(sample_data_k)
sample_data_k$workclass=as.numeric(sample_data_k$workclass)
sample_data_k$education=as.numeric(sample_data_k$education)
sample_data_k$marital.status=as.numeric(sample_data_k$marital.status)
sample_data_k$occupation=as.numeric(sample_data_k$occupation)
sample_data_k$relationship=as.numeric(sample_data_k$relationship)
sample_data_k$race=as.numeric(sample_data_k$race)
sample_data_k$sex=as.numeric(sample_data_k$sex)
sample_data_k$native.country=as.numeric(sample_data_k$native.country)

```

```{r}
set.seed(0040)
index=sample(c(1:r),size = 0.8*r,replace = F)
train=sample_data_k[index,]
test=sample_data_k[-index,]
```

```{r}
train_features=train[,-c(c)]
train_label=train[,c(c)]
test_features=test[,c(-c)]
test_label=test[,c(c)]

k=3
```

```{r}
model3=knn(train = train_features,test = test_features,cl=train_label,k=5)
```

```{r}
confmat=table(model3,test_label)
confmat
```

```{r}
Accuracy=sum(diag(confmat))/sum(confmat)
#Accuracy = (count/length(pc_pred_label))*100
paste("Accuracy of kNN : ",Accuracy*100)
```


